Trends of downward SDR in Thessaloniki

### 2023-05-05 Article.Rmd
Commit 2023-04-28 13:17
Commit 2023-05-02 13:17
Commit 2023-05-05 10:17

```{r echo=F, include=F, cache=T}
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = '!h'    )

```

```{r echo=F, include=T}
## variables we use
source("~/MANUSCRIPTS/2022_sdr_trends/DHI_GHI_0_variables.R")
```

@@

<!-- time span -->
Time span for CM-21 is 1993-2022 and 2016-2022 for CHP-1.

goal

basic conceptions

@@

<!-- Seasonal -->
..... Define seasons aggregation if used .......

@@

@@

@@

```{r seasonalALL, echo=F, fig.cap="Donditions."}
knitr::include_graphics("./images/SeasonaltTrends-1.pdf")
```

```{r seasonalCLEAR, echo=F, fig.cap="Daiditions."}
knitr::include_graphics("./images/SeasonaltTrends-2.pdf")
```

```{r seasonalCLOUD, echo=F, fig.cap="Daiditions."}
knitr::include_graphics("./images/SeasonaltTrends-3.pdf")
```

@@

>>>>

```{r echo=F, include=T}
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = '!h'    )
library(pander)
library(data.table)
## load data
load("./data/common_data_14_2.Rda")
## variables we use
source("~/MANUSCRIPTS/2022_sdr_trends/DHI_GHI_0_variables.R")
```

@@

<!-- time span -->
The global radiation was obtained from the pyranometer CM-21, for the period
`r min(ALL_1_daily_DESEAS$Date)` -  `r max(ALL_1_daily_DESEAS$Date)`.
In some algorithms we used direct radiation data for comparisons, obtained by a CM-21 pyrheliometer, with data span
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])` - `r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.

<!-- goals -->
Here we investigate the trend on shortwave radiation for the last decades at Thessaloniki, and try to infer a relation to sky conditions (all, clear, cloudy).

<!-- basic concepts -->
The approach of our method to characterize the sky conditions and the definition of each sky condition has some ......μη αντικειμένικότητα

@@

<!-- Seasonal -->
For the seasons of the year trends we grouped the mean daily values by season (December - February: Winter, March - May: Spring, etc.)

@@

\footnotesize
```{r trendtable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("Global" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp) <- NULL
names(pp) <- c("Trend %/year", "Trend p-value", "Sky condition", "Trend statistical significance")

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "Trends of daily means by sky conditions.")
```
\normalsize

@@

```{r seasonalALL, echo=F, fig.cap="Trends by season for All-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonaltTrends-1.pdf")
```

```{r seasonalCLEAR, echo=F, fig.cap="Trends by season for Clear-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonaltTrends-2.pdf")
```

```{r seasonalCLOUD, echo=F, fig.cap="Trends by season for Cloudy-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonaltTrends-3.pdf")
```

\footnotesize
```{r trendseasontable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("Global" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp) <- NULL
names(pp) <- c("Trend %/year", "Trend p-value", "Sky condition", "Season", "Trend statistical sign.")

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "Trends of daily means by sky conditions.")
```
\normalsize

@@

@@

```{r cm, echo=F, fig.cap="Donditions."}
knitr::include_graphics("./images/CumulativeDailyCumSum-1.pdf")
```
